DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-09 Examples/PDE/InstatPDE/Example6/content.tex
Update Doku und Beseitigung kleinerer Doku-typos in zwei main files.

\subsubsection{General problem description}
The modeling part of this example is based on the coupled
Biot-Lam\'e-Navier system, 
which is a standard model in subsurface modeling. 
Here, a reservoir (the
pay-zone) is modeled as a poroelastic medium with the help of Biot's
equations. A surrounding medium (the non-pay zone) is modeled as a static
elastic solid. 
In fact, the
Biot system is a multi-scale problem which 
is identified on the micro-scale as 
a fluid-structure interaction problem (details on the 
interface law are found in Mikeli\'c and Wheeler (2011). 
This system 
is specifically suited for applications 
in subsurface modeling for the poroelastic part, the 
so-called pay-zone.  
On the other hand, surrounding rock 
(the non-pay zone) 
is modeled with the help of linear elasticity (Ciarlet 1984). 
Therefore, the final configuration 
belongs to a multiphysics problem in non-overlapping domains.
The nonstationary coupled system for the state is formulated 
within a variational monolithically-coupled framework, 
which is known 
to be more robust than partitioned solutions algorithms.
Its discretization 
is carried out with help of the Rothe method in which we first 
discretize in time and then in space. 
The configuration 
is based on the augmented Mandel problem which 
shows the important Mandel-Cryer effect: First increasing pressure
and then decreasing pressure in time while applying some 
traction force on the top boundary.

>>>>

\subsubsection{General problem description}
The modeling part of this example is based on the coupled
Biot-Lam\'e-Navier system. The Biot system itself   
is a standard model in subsurface modeling \cite{Biot41a, Biot41b, Biot55}. 
Here, a reservoir (the
pay-zone) is modeled as a poroelastic medium with the help of Biot's
equations. A surrounding medium (the non-pay zone) is modeled as a static
elastic solid. 
In fact, the
Biot system is a multi-scale problem which 
is identified on the micro-scale as 
a fluid-structure interaction problem (details on the 
interface law are found in Mikeli\'c and Wheeler (2011). 
This system 
is specifically suited for applications 
in subsurface modeling for the poroelastic part, the 
so-called pay-zone.  
On the other hand, surrounding rock 
(the non-pay zone) 
is modeled with the help of linear elasticity (Ciarlet 1984). 
Therefore, the final configuration 
belongs to a multiphysics problem in non-overlapping domains.
The nonstationary coupled system for the state is formulated 
within a variational monolithically-coupled framework, 
which is known 
to be more robust than partitioned solutions algorithms.
Its discretization 
is carried out with help of the Rothe method in which we first 
discretize in time and then in space. 
The configuration 
is based on the augmented Mandel problem which 
shows the important Mandel-Cryer effect: First increasing pressure
and then decreasing pressure in time while applying some 
traction force on the top boundary.
